{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-21 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, phrasing things better, sync

    \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
        Suppose $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are R-WAPG sequences given by Definition \ref{def:rwapg-seq}, and they are constant meaning that there exists $\rho, \alpha$ such that $\alpha_k := \alpha$ and $\rho_k := \rho$ for all $k \ge 0$.
        Define the momentum term $\theta = \rho\alpha(1 - \alpha)/(\rho\alpha^2 + \alpha)$. 
        Then the constant R-WAPG sequence satisfies: 
        \begin{enumerate}
            \item $\rho = (1 - \mu/L\alpha^{-1})/(1 - \alpha)$. 
            \item $\theta = (1 - \alpha)(1 - \mu/L \alpha^{-1})/(1 - \mu/L)$. 
            \item For any $r \in \left(\sqrt{\mu/L}, \sqrt{L/\mu}\right)$, let $\alpha = r \sqrt{\mu/L}$. If $\sqrt{L/\mu} > r > 1$, then $\rho > 1$ else if $\sqrt{\mu/L} < r \le 1$ then $\rho \in (0, 1]$. 
            \item If $\alpha = \sqrt{\mu/L}$, then $\rho = 1$, $\theta = \left(1 - \sqrt{\mu/L}\right)/\left(1 + \sqrt{\mu/L}\right)$. 
        \end{enumerate}
    \end{lemma}
    \begin{proof}
        It's direct to show (i). 
        By the definition of $(\rho_k)_{k\ ge0}$ in the R-WAPG sequence definition, we have 
        \begin{align*}
            \rho_k &= 
            \frac{\alpha_{k + 1}^2 - \mu/L \alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2}
            = 
            \frac{\alpha^2 - \mu/L \alpha}{(1 - \alpha)\alpha^2}
            \\
            &= \frac{1 - (\mu/L)\alpha^{-1}}{1 - \alpha}. 
        \end{align*}
        To see (ii), it's direct by the definition of $\theta$: 
        \begin{align*}
            \theta &= 
            \frac{\rho \alpha(1 - \alpha)}{\rho \alpha^2 + \alpha} 
            = 
            (\rho \alpha)\frac{(1 - \alpha)}{\rho \alpha^2 + \alpha}
            \\
            &= \left(
                \frac{\alpha - (\mu/L)}{1 - \alpha}
            \right)\frac{(1 - \alpha)}{\alpha \frac{\alpha - \mu/L}{1 - \alpha} + \alpha}
            = \frac{\alpha - \mu/L}{\alpha\left(\frac{\alpha - \mu/L}{1 - \alpha}\right)+ \alpha}
            \\
            &= \left(1 - \mu/L \alpha^{-1}\right)\left(
                \frac{\alpha - \mu/L}{1 - \alpha} + 1
            \right)^{-1} 
            \\
            &= 
            \frac{(1 - \alpha)\left(1 - \mu/L \alpha^{-1}\right)}{1 - \mu/L}. 
        \end{align*}
        To see (iii), we substitute $\alpha = r \sqrt{\mu/L}$ into the expression for $\rho$ in (i) which gives: 
        \begin{align*}
            \rho_k &= \frac{1 - \mu/L\alpha^{-1}}{1 - \alpha} 
            = \frac{1 - r^{-1}\left(\mu/L\sqrt{L/\mu}\right)}{1 - r \sqrt{\mu/L}} 
            = \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r \sqrt{\mu/L}}. 
        \end{align*}
        If $\sqrt{L/\mu}> r > 1$ then $\rho > 1$ because 
        \begin{align*}
            \rho &= \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r \sqrt{\mu/L}} 
            > \frac{1 - \sqrt{\mu/L}}{1 - \sqrt{\mu/L}} = 1. 
        \end{align*}
        When $\sqrt{\mu/L} < r < 1$, it has 
        \begin{align*}
            0 < 1 - r^{-1}\sqrt{\mu/L} < \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r\sqrt{\mu/L}} = \rho < \frac{1 - \sqrt{\mu/L}}{1 - \sqrt{\mu/L}} = 1. 
        \end{align*}
        The first inequality used $r > \sqrt{\mu/L}$. 
        The third inequality used $r < 1$. 
        To see (iv), substitute $\alpha = \sqrt{\mu/L}$ for $\rho$.

>>>>

    \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
        Suppose $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are R-WAPG sequences given by Definition \ref{def:rwapg-seq} and assume $L > \mu > 0$.
        Define $q := \mu/L$. 
        Then $\forall r \in \left(\sqrt{q},\sqrt{q^{-1}}\right)$, the constant sequence $\alpha_k := r \sqrt{q}$ is a valid R-WAPG sequence and it has

        % Define the momentum term $\theta = \rho\alpha(1 - \alpha)/(\rho\alpha^2 + \alpha)$. 
        % Then the constant R-WAPG sequence satisfies: 
        % \begin{enumerate}
        %     \item $\rho = (1 - \mu/L\alpha^{-1})(1 - \alpha)^{-1}$. 
        %     \item $\theta = (1 - \alpha)(1 - \mu/L \alpha^{-1})(1 - \mu/L)^{-1}$. 
        %     \item For any $r \in \left(\sqrt{\mu/L}, \sqrt{L/\mu}\right)$, let $\alpha = r \sqrt{\mu/L}$. If $\sqrt{L/\mu} > r > 1$, then $\rho > 1$ else if $\sqrt{\mu/L} < r \le 1$ then $\rho \in (0, 1]$. 
        %     \item If $\alpha = \sqrt{\mu/L}$, then $\rho = 1$, $\theta = \left(1 - \sqrt{\mu/L}\right)/\left(1 + \sqrt{\mu/L}\right)$. 
        % \end{enumerate}
    \end{lemma}
    \begin{proof}
        It's direct to show (i). 
        By the definition of $(\rho_k)_{k\ ge0}$ in the R-WAPG sequence definition, we have 
        \begin{align*}
            \rho_k &= 
            \frac{\alpha_{k + 1}^2 - \mu/L \alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2}
            = 
            \frac{\alpha^2 - \mu/L \alpha}{(1 - \alpha)\alpha^2}
            \\
            &= \frac{1 - (\mu/L)\alpha^{-1}}{1 - \alpha}. 
        \end{align*}
        To see (ii), it's direct by the definition of $\theta$: 
        \begin{align*}
            \theta &= 
            \frac{\rho \alpha(1 - \alpha)}{\rho \alpha^2 + \alpha} 
            = 
            (\rho \alpha)\frac{(1 - \alpha)}{\rho \alpha^2 + \alpha}
            \\
            &= \left(
                \frac{\alpha - (\mu/L)}{1 - \alpha}
            \right)\frac{(1 - \alpha)}{\alpha \frac{\alpha - \mu/L}{1 - \alpha} + \alpha}
            = \frac{\alpha - \mu/L}{\alpha\left(\frac{\alpha - \mu/L}{1 - \alpha}\right)+ \alpha}
            \\
            &= \left(1 - \mu/L \alpha^{-1}\right)\left(
                \frac{\alpha - \mu/L}{1 - \alpha} + 1
            \right)^{-1} 
            \\
            &= 
            \frac{(1 - \alpha)\left(1 - \mu/L \alpha^{-1}\right)}{1 - \mu/L}. 
        \end{align*}
        To see (iii), we substitute $\alpha = r \sqrt{\mu/L}$ into the expression for $\rho$ in (i) which gives: 
        \begin{align*}
            \rho_k &= \frac{1 - \mu/L\alpha^{-1}}{1 - \alpha} 
            = \frac{1 - r^{-1}\left(\mu/L\sqrt{L/\mu}\right)}{1 - r \sqrt{\mu/L}} 
            = \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r \sqrt{\mu/L}}. 
        \end{align*}
        If $\sqrt{L/\mu}> r > 1$ then $\rho > 1$ because 
        \begin{align*}
            \rho &= \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r \sqrt{\mu/L}} 
            > \frac{1 - \sqrt{\mu/L}}{1 - \sqrt{\mu/L}} = 1. 
        \end{align*}
        When $\sqrt{\mu/L} < r < 1$, it has 
        \begin{align*}
            0 < 1 - r^{-1}\sqrt{\mu/L} < \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r\sqrt{\mu/L}} = \rho < \frac{1 - \sqrt{\mu/L}}{1 - \sqrt{\mu/L}} = 1. 
        \end{align*}
        The first inequality used $r > \sqrt{\mu/L}$. 
        The third inequality used $r < 1$. 
        To see (iv), substitute $\alpha = \sqrt{\mu/L}$ for $\theta$ as defined in (i): 
        \begin{align*}
            \theta &= \frac{(1 - \alpha)(1 - \mu/L \alpha^{-1})}{1 - \mu/L}
            = \frac{(1 - \sqrt{\mu/L})(1 - \sqrt{\mu/L})}{1 - \mu/L}
            \\
            &= \frac{1 - \sqrt{\mu/L}}{1 + \sqrt{\mu/L}}. 
        \end{align*}
